### 2012-03-29 contents.tex
Fixing problem with margins (reported by the Conference Publishing script). Camera ready copy.

\begin{figure}[ht]
	\centering
		\includegraphics[width=0.48\textwidth]{bugzilla}
	\caption{Simplified workflow for Bugzilla. Adapted from \url{http://www.bugzilla.org/docs/2.18/html/lifecycle.html}.}
	\label{fig:bugzilla}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{when}
% \mbox{
% \subfigure{\includegraphics[width=0.25\textwidth]{milestones}}%\quad
% \subfigure{\includegraphics[width=0.25\textwidth]{cliffs} }}
\caption{Accumulated number of verifications over time.} \label{fig:when}
\end{figure}

@@

	\begin{table}
		\begin{center}

@@

	\begin{table}
		\begin{center}
		\caption{Verification techniques for all four subprojects.} \label{tab:how}
		\begin{tabular}{l|r|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering Testing} & 
			\textbf{\centering Inspection} & 
			\textbf{\centering Ad Hoc} \\
			\hline
			Eclipse/Platform        & 250 (1.1\%) & 511 (2.2\%) & 67 (0.3\%) \\
			Eclipse/EMF             & 21 (1.6\%) & 1 (0.1\%) & 0 \hspace{0.8cm} \\
			NetBeans/Platform       & 88 (0.8\%) & 5 (0.0\%) & 0 \hspace{0.8cm} \\
			NetBeans/VersionControl & 4 (0.1\%) & 1 (0.0\%) & 0 \hspace{0.8cm}
			% \bottomrule
		\end{tabular}
		\end{center}
	\end{table}

@@

%\small{
This work is supported by FAPESB under grant BOL0119/2010 and by CNPq/INES under grant 573964/2008-4.% er wer wer wer we rwe rwe rwe rwe rwe rw erw er wer wer wer wer wer wer wer wer  qwe qwe qwe qwe qwe qwe qwe qw eqwe  qwe qwe qwe qwe q qwe qwe qwe qw e
%}

>>>>

\begin{figure}[ht]
	\centering
	\vspace{2mm}
		\includegraphics[width=0.48\textwidth]{bugzilla}
	\caption{Simplified workflow for Bugzilla. Adapted from \url{http://www.bugzilla.org/docs/2.18/html/lifecycle.html}.}
	\label{fig:bugzilla}
\end{figure}

@@

\begin{figure}
\centering
\vspace{2mm}
\includegraphics[width=0.48\textwidth]{when}
% \mbox{
% \subfigure{\includegraphics[width=0.25\textwidth]{milestones}}%\quad
% \subfigure{\includegraphics[width=0.25\textwidth]{cliffs} }}
\caption{Accumulated number of verifications over time.} \label{fig:when}
\end{figure}

@@

	\begin{table}
		\vspace{2mm}
		\begin{center}

@@

	\begin{table}
		\begin{center}
		\vspace{2mm}
		\caption{Verification techniques for all four subprojects.} \label{tab:how}
		\begin{tabular}{l|r|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering Testing} & 
			\textbf{\centering Inspection} & 
			\textbf{\centering Ad Hoc} \\
			\hline
			Eclipse/Platform        & 250 (1.1\%) & 511 (2.2\%) & 67 (0.3\%) \\
			Eclipse/EMF             & 21 (1.6\%) & 1 (0.1\%) & 0 \hspace{0.8cm} \\
			NetBeans/Platform       & 88 (0.8\%) & 5 (0.0\%) & 0 \hspace{0.8cm} \\
			NetBeans/VersionControl & 4 (0.1\%) & 1 (0.0\%) & 0 \hspace{0.8cm}
			% \bottomrule
		\end{tabular}
		\end{center}
	\end{table}

@@

\small{
This work is supported by FAPESB under grant BOL0119/2010 and by CNPq/INES under grant 573964/2008-4.% er wer wer wer we rwe rwe rwe rwe rwe rw erw er wer wer wer wer wer wer wer wer  qwe qwe qwe qwe qwe qwe qwe qw eqwe  qwe qwe qwe qwe q qwe qwe qwe qw e
}
